Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-05-23 manuscript.tex
reword and fix figure caption

\begin{figure}
    \subcaptionbox{Position space view of reachability sets\label{fig:varying_tf_trajectory}}{\includegraphics[width=0.5\textwidth]{figures/l1_transfer/trajectory_varying_um.pdf}}~
    \subcaptionbox{\Poincare section view of reachability sets\label{fig:varying_tf_poincare}}{\includegraphics[width=0.5\textwidth]{figures/l1_transfer/poincare_section_varying_um.pdf}}
    \caption{Variation of \( t_f \) and \( u_m\) on the reachability set. 
    Colors, \braces{red, blue, green, yellow}, are used note increasing \( t_f\) while markers, \braces{circle, square, cross}, are used to denote increasing \(u_m\).
    Increasing the maximum control bound has a large effect and enables the reachability set to intersect the target manifold. 
    Increases in \(t_f\) are less critical and have minimal impact on the distribution of the reachability set on the \Poincare section.~\label{fig:varying_tf_reachability_sets}}
\end{figure}

\Cref{fig:varying_tf_reachability_sets} shows the reachabilty set for twelve combinations of \(t_f\) and \( u_m\) listed in~\cref{tab:varying_tf}.
With a small maximum control bound, \( u_m = \num{0.05} \) shown using square markers, the reachable set is not dramatically changed from that of the no control solution.
The reachable set is denoted using square markers on the left most portion of \cref{fig:varying_tf_poincare}.
Variations of \( t_f\) are indicated using different colors and also demonstrate that this parameters has a smaller impact than changes in \( u_m \).
Increasing the control bound to \( u_m = \num{0.25} \) and \( u_m = \num{0.5} \) shows that the reachable set is progressively approaching the target set and there are several intersections.

>>>>

\begin{figure}
    \subcaptionbox{Position space view of reachability sets\label{fig:varying_tf_trajectory}}{\includegraphics[width=0.5\textwidth]{figures/l1_transfer/trajectory_varying_um.pdf}}~
    \subcaptionbox{\Poincare section view of reachability sets\label{fig:varying_tf_poincare}}{\includegraphics[width=0.5\textwidth]{figures/l1_transfer/poincare_section_varying_um.pdf}}
    \caption{Variation of \( t_f \) and \( u_m\) on the reachability set. 
        Colors, \braces{\text{red}, \text{blue}, \text{green}, \text{yellow}}, are used note increasing \( t_f\) while markers, \braces{\text{circle}, \text{square}, \text{cross}}, are used to denote increasing \(u_m\).
    Increasing the maximum control bound has a large effect and enables the reachability set to intersect the target manifold. 
    Increases in \(t_f\) are less critical and have minimal impact on the distribution of the reachability set on the \Poincare section.~\label{fig:varying_tf_reachability_sets}}
\end{figure}

\Cref{fig:varying_tf_reachability_sets} shows the reachabilty set for twelve combinations of \(t_f\) and \( u_m\) listed in~\cref{tab:varying_tf}.
With a small maximum control bound, \( u_m = \num{0.05} \) shown using square markers, the reachable set is not dramatically changed from that of the no control solution.
The reachable set is denoted using square markers on the left most portion of \cref{fig:varying_tf_poincare}.
Variations of \( t_f\) are indicated using different colors and also demonstrate that this parameters has a smaller impact than changes in \( u_m \).
Increasing the control bound to \( u_m = \num{0.25} \) and \( u_m = \num{0.5} \) shows that the reachable set progressively approaches the target set.
